---
title: "Lab 10 - cool and sometimes useful things"
author: "Renee LaManna"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(usethis)
library(janitor)

# New packages
library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
```

## beeper beeps

Use the fxn `beep()` in the beepr package to make an audio alert when your code is done running. 
- Run beep in console(1-12) pick a  number 1-12
- **paste default indicates 1 space between number in sequence and first word e.g. paste0 -> 99bottles
- want code to exist, but don't want to run code everytime, eval = FALSE

```{r eval = FALSE}
for (i in rev(seq(1:99))) {
  
  print(paste(i, "bottles of beer on the wall"))
}

beep(4)

```

## Praise and cowsay 

Packages built with a single purpose: to be kind and fun.

```{r}
praise("${Exclamation},
       ${EXCLAMATION}... ${exclamation}!!!!")
       
praise("Holy ${creating}, Batman - this code is ${ADJECTIVE}!")
```

Use cowsay::say()

```{r}

```

>  in console to convert to git

usethis::use_git, yes, yes
and then  usethis::use_git() again in console
- should pull up online tab
- can rename branch in github, but won't rename in local
- must copy and paste link
- "git branch -m master main
git fetch origin
git branch -u origin/main main
git remote set-head origin -a" run without quotes in terminal



## Use paletteer to access thousand of color palettes

```{r}
storms %>% 
  group_by(name) %>% 
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>% 
  slice_min(n = 10, min_pressure) %>% 
  ggplot(aes(x = min_pressure, y = name)) +
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("colRoz::desert_dusk")
  
```

## One spatial data example
NA is a constant NOT a variable, so color = NA applies to line color

```{r}
vegetation <- read_sf("doc.kml") %>% 
  clean_names() %>% 
  select(name) 

ggplot(data = vegetation) +
  geom_sf(aes(fill = name), color = NA) +
  theme_minimal() +
  scale_fill_paletteer_d("ggthemes::manyeys") +
  labs(title = "Jornada Basin LTER Vegetation",
       caption = "Source: Jornada LTER")
  
# Update to theme_minimal
# Fill color change based on vegetation
# color of line to NA (color = NA)
```
```{r}
ggsave(filename = "my_awesome_map.jpg", width = 8, height = 5)
```

